---
title: "task_2"
author: "CKH21"
format: html
editor: 
  markdown: 
    wrap: sentence
---

## Requirements

Your analysis should produce a single, main result in terms of statistical families of z-, t-, F-, or χ² tests (or their alternative or non-parametric versions).

You **should not control** for age, gender, education, employment (a proxy for income), urban vs. rural locations, victimization by violence, property damage due to violence, and displacement by violence.
You should not use Tobit Regression in your analysis.

## Load packages

```{r}
#| message: false
library(here)
library(foreign)

library(psych)
library(here)

library(tidyverse)

library(ggstatsplot)
library(ggdist)
library(stargazer)

library(performance)

library(coin)
library(dunn.test)
library(rstatix)
```

## Read Data

Let's start by reading the original data

```{r}
here()
df <- read.dta(file = "data/JEPS_replication_data.dta") |> 
    mutate(regions = regions |> 
           factor(levels = c("Primarily Serb region", 
                             "Border region",
                             "Primarily Albanian region")))
```

1.  d12outgroup = amount sent in the dictator game to an out-group recipient.

2.  regions = three category variable for location of subjects (0 = Primarily Albanian region, 1 = border region, 2 = Primarily Serb region).
    This variable is used to make the box-whisker plot in the manuscript.

## independence test

In order to check the original claim " out-group bridging \... norms increase with exposure to the out-group" we will use permutation alternative to anova as a heuristic for the following analysis and test whether amount of money gifted to out group increases with exposure to out-group.

```{r}
df |>  
  independence_test(d12outgroup ~ regions, data = _,
                    alternative = "greater") 
```

After spotting the difference, we could do all statistical rituals to decide if we could or could not use ANOVA, but hopefully the outcome remain untouched.

### test normality of groups

```{r}
df |> 
  filter(regions == "Primarily Serb region") |> 
  pull(d12outgroup) |> 
  shapiro.test()

df |> 
  filter(regions == "Border region") |> 
  pull(d12outgroup) |> 
  shapiro.test()

df |> 
  filter(regions == "Primarily Albanian region") |> 
  pull(d12outgroup) |> 
  shapiro.test()

df |> 
  ggplot(aes(y = regions, x = d12outgroup, fill = regions)) +
  stat_slab(aes(thickness = after_stat(pdf*n)), scale = 0.7) +
  stat_dotsinterval(side = "bottom", scale = 0.7, slab_linewidth = NA) +
  scale_fill_brewer(palette = "Set2")+
  theme_minimal()+
  theme(legend.position = "bottom")

```

The amount of money from 0 to 5, gifted to out group is obviously non normally distributed, and that is a violation of the classical ANOVA.

### test  homogeneity of variances

```{r}
df |> 
  bartlett.test(d12outgroup ~ regions, data = _)
```

However, Variance among groups is most likely equal, so we are not violating this assumption, and could safely use non-parametric

### A non-parametric equivalent to one-way ANOVA (kruskal_test)

```{r}
df |> 
  coin::kruskal_test(d12outgroup ~ regions, data = _,
              var.equal = TRUE)
```

The difference in median among groups is statistically significant, so that we could move for pairwise comparison of groups.

### Post-hoc

```{r}
?dunn_test
df |> 
  dunn_test(d12outgroup ~ regions, data = _, detailed = TRUE) |> 
  kableExtra::kable()
```

Dunn test provides evidence that there is a difference in median amount gifted to out group between Serbians who live in *Primarily Serb region* and *Primarily Albanian region.*

```{r}
df |> 
  ggbetweenstats(x = regions,
                 y = d12outgroup,
                 ylab = "out-group bridging norms (gifting to out-group)",
                 violin.args = list(width = 0),
                 type = "np")
```

We could clearly visualize the difference in medians, and with good certainty claim that **out-group bridging norms** (measured as amount gifted to out-group) **increase with exposure to the out-group** (approximated by place of living) for Serbians.
